TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project Proposal}

### 2017-11-17 initial.tex
m. Mainly cosmetic changes to planning

\begin{tabular}[H]{ | l | p{10cm} | }
	\hline
	\textbf{Week} & \textbf{Activity} \\
	\hline 1 & Conducting desk research on TCP congestion control algorithms. Conducting desk research on the congestion and packet loss occuring in different scenarios. Conducting desk research on bandwidth management in data centers. Setup the testing environment. \\
	\hline 2 & Finish test environment setup and conduct all tests.\\
	\hline 3 & Process the results and start writing the project report. \\
	\hline 4 & Finalize our project report and process the final results. Setting up the presentation and practice it. \\
	\hline
\end{tabular}

>>>>

\begin{tabular}[H]{ | l | p{10.2cm} | }
	\hline
	\textbf{Week} & \textbf{Activity} \\
	\hline 1 & Conducting desk research on: which TCP congestion control algorithms are used the most, packet loss occuring in different scenarios, and existing bandwidth management in data centers. We will also setup the testing environment. \\
	\hline 2 & Finish test environment setup and conduct tests. \\
	\hline 3 & Process the results and start writing the project report. \\
	\hline 4 & Process the final results, finalize our project report and prepare the presentation. \\
	\hline
\end{tabular}
